Curve counting in genus one: \\ elliptic singularities {\it \&} relative geometry

### 2021-03-28 EllipticSingularitiesSplitting.tex
Added keywords etc.

@@

\noindent Luca Battistella\\
Mathematisches Institut, Universit\"at Heidelberg \\
\href{mailto:lbattistella@mathi.uni-heidelberg.de}{lbattistella@mathi.uni-heidelberg.de}\\

\noindent Navid Nabijou \\
Department of Pure Mathematics and Mathematical Statistics, University of Cambridge \\
\href{mailto:nn333@cam.ac.uk}{nn333@cam.ac.uk}\\

\noindent Dhruv Ranganathan \\
Department of Pure Mathematics and Mathematical Statistics, University of Cambridge \\
\href{mailto:dr508@cam.ac.uk}{dr508@cam.ac.uk}

>>>>

\footnotetext{\emph{2020 Mathematics Subject Classification.} Primary: 14N35. Secondary: 14H10.\\ \emph{Keywords:} enumerative geometry, logarithmic Gromov--Witten theory, elliptic singularities, quantum Lefschetz.}

@@

\noindent Luca Battistella\\
Mathematisches Institut, Ruprecht-Karls-Universit\"at Heidelberg, Im Neuenheimer Feld 205, 69120 Heidelberg, Germany \\
\href{mailto:lbattistella@mathi.uni-heidelberg.de}{lbattistella@mathi.uni-heidelberg.de}\\

\noindent Navid Nabijou \\
Department of Pure Mathematics and Mathematical Statistics, University of Cambridge, Centre for Mathematical Sciences, Wilberforce Road, Cambridge CB3 0WB, United Kingdom \\
\href{mailto:nn333@cam.ac.uk}{nn333@cam.ac.uk}\\

\noindent Dhruv Ranganathan \\
Department of Pure Mathematics and Mathematical Statistics, University of Cambridge, Centre for Mathematical Sciences, Wilberforce Road, Cambridge CB3 0WB, United Kingdom \\
\href{mailto:dr508@cam.ac.uk}{dr508@cam.ac.uk}
